\thetitle

### 2020-08-15 writing/discussion.tex
discussion: transient blame TR vs RP

>>>>

\subsection{Threat: Is our Transient Correct?}
%% purpose: talk about transient-blame implementation .... what did we do,
%%  how did we test, what threats remain?
%%
%% the benchmark timeouts look like a threat, but this section shows that
%%  we've looked carefully at those

An apparent flaw in our transient is the high cost of blame.
Whereas \citet{vss-popl-2017} report an average slowdown of 2.5x and
 worst-case of 5.4x on fully-typed benchmarks in Reticulated,
 our configurations frequently exceed a 10 minute timeout with transient blame.
Unfortunately, our high cost is closer to the truth;
 Reticulated has two advantages that give low overhead in the prior work.
First, Reticulated's type inference often assigns the dynamic type to local
 variables in "fully typed" code.
This flexible type gives a programmer fewer static errors and less-precise
 blame,; but it also makes the benchmarks run faster.
Second, \citet{vss-popl-2017} use relatively small benchmarks.
Four have since been retired from the official Python benchmark suite
 because they are too small, unrealistic, and unstable.
On larger programs, Reticulated suffers from high overhead.
For example, a Reticulated version of our \texttt{sieve} benchmark runs in
 ~40 seconds without blame, and with blame times out after 10 minutes.

%% NOTE: Vitousek's benchmarks are from the Python "pyperformance" suite.
%%   The version notes in the docs talk about retiring benchmarks, but
%%   you can also look at the current codebase and see what names from POPL'17
%%   are missing: callsimple, callmethod, callmethodslots, & pystone
%% <https://github.com/python/pyperformance/tree/master/pyperformance/benchmarks>
